Next Trippy Structures\thanks{Supported by organization x.}

### 2019-06-11 paper.tex
Add T-Matrices spaces

\subsection{Space requirements}
\label{sec:space}
We have measured the sizes of all the individual components of our representation in memory when built over the experimental dataset. We present the sizes of our common structures, followed by the \acumm\marginpar{Missing \acumm~sizes!}. After that, we compare the compression achieved with \ttctr~and \ctr.

@@

>>>>

\subsection{Space requirements}
\label{sec:space}
We have measured the sizes of all the individual components of our representation in memory when built over the experimental dataset. We present the sizes of our common structures, followed by the \acumm. After that, we compare the compression achieved with \ttctr~and \ctr.

@@

To measure the sizes occupied by the different variants of \acumm~that were presented in Section~\ref{sec:acumm}, we have summed the total space required by each line matrix. These results, which can be found in Table~\ref{tab:acuum}, helped us prove that \texttt{Blocks} is an effective strategy to reduce the size of the accumulated values. While \texttt{Diff} is also able to reduce the total space, it's fundamentally constrained by the shape of our matrices, making it less desirable in this context.

\begin{table}
    \centering
    \caption{Sizes of the different variants from \acumm}
    \label{tab:acuum}
    \begin{tabular}{|c|c|c|c|}
    \hline
        Variant & \texttt{Sum} & \texttt{Diff} & \texttt{Blocks} \\
        \hline
        Size (MiB) & 55.49 & 43.81 & 28.68 \\
    \hline
    \end{tabular}
\end{table}
